Verifying Spatial Properties of Array Computations

### 2017-04-13 oopsla17/oopsla17.tex
expanding hypotheses

\begin{enumerate}
\item Stencils are ubiquitious;
\item Most stencils read their data from source arrays with a static pattern
base on constant offsets from the mid-point;
\item Most stencils read their data from contiguous \emph{regions} in an array;
\item Most stencils read each index at most once.
\end{enumerate}

>>>>

Hypotheses:
\begin{enumerate}
\item Loops over arrays mainly read from arrays with a static pattern
based on constant offsets from (base or dervied) induction variables;

\item Most loop-array computations of the previous form read
from a arrays with a contiguous pattern;

\item Many array computations are \emph{stencil computations},
with a static access pattern, writing
to an array at an index based on a constant offset from induction
variables.

\item Many array computations read from a particular index just once
\end{enumerate}
